Gait Monitoring using Wireless Sensors\\ \vspace{4mm} \large{Final Report 18-748}\\ \large{Spring 2017}

### 2017-05-10 paper.tex
Added conclusion and milestones

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\columnwidth]{figs/gui}
  \caption{{\bf ROS user interface}}
  \label{fig:gui}
\end{figure}
The user interface also provides a convenient video playback feature than can replay all
of the data visualizations produced in real time during active data capture as well as an
accompanying video of the subject. Finally, the data are logged automatically for future
use or offline analyses.

@@

\section{Conclusion}

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=\columnwidth]{figs/gui}
  \caption{{\bf ROS user interface}}
  \label{fig:gui}
\end{figure}
The user interface also provides a convenient video playback feature than can replay all
of the data visualizations produced in real time during active data capture as well as an
accompanying video of the subject. Finally, the data are logged automatically for future
use or offline analyses.

@@

\section{Conclusion}
\sys is a proof-of-concept implementation of gait monitoring using low cost IMUs and
a small number of wireless sensors. We were able to measure relevant parameters of our
subject's gaits and visualize the data in an accessible fashion despite the relatively low
data transfer rate in our network. \sys represents an example of a low cost monitoring
solution for patients with fall risks, and it could provide additional data for healthcare
providers seeking to customize a plan of care to a patient's behavior outside of the
office. We worked through several major challenges including timing mismatch between the
IMU and the Firefly, packet loss in the network, IMU drift, and signal processing
subtleties.
\section{Milestones and Task Division}
We achieved most of the milestones that we set out to accomplish in our original project
proposal, though some of the deadlines for the different milestones shifted.
Figure~\ref{fig:table} is a timeline of our original deliverable schedule and an explanation
of when each deliverable was finished or how it changed.

\begin{figure}[h]
  \centering
  \includegraphics[width=\columnwidth]{figs/table}
  \caption{{\bf Timeline of deliverables }}
  \label{fig:table}
\end{figure}

The table below reports the segments of the project each team member completed.\\
\begin{tabular}{|p{.95\columnwidth}|}
  \hline
{\bf Alex:}
\begin{itemize}
  \item {IMU calibration feasibility assessment}
  \item ROS system development and management
  \item Motion capture and visualization
\end{itemize}\tabularnewline
\hline
{\bf Emily:}
\begin{itemize}
  \item{Data transfer from IMU to Firefly}
  \item{Inter-Firefly communication management}
  \item{Final report organization} 
\end{itemize}\tabularnewline
\hline
{\bf Iljoo:}
\begin{itemize}
  \item{Knee extension calculation} 
  \item{Step detection research and implementation}
  \item{Enclosure fabrication} 
\end{itemize}\tabularnewline
  \hline
\end{tabular}
